Predicting information integration in pragmatic word learning across development

### 2021-03-31 papers/full_paper/manuscript.Rmd
add first draft BDA figure

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "manuel_bohn@eva.mpg.de"
  - name          : "Michael Henry Tessler"
    affiliation   : "2"
  - name          : "Megan Merrick"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    affiliation   : "3"

@@

keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling, common ground"
wordcount         : "7708"

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

@@

@@

# Acknowledgments

We thank Jacqueline Quirke and Sabina Zacco for help with the data collection and Bria Long and Gregor Kachel for comments on an earlier version of the paper.

# Funding

M. Bohn received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no. 749229. M. C. Frank was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.

>>>>

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig"
    email         : "manuel_bohn@eva.mpg.de"
  - name          : "Michael Henry Tessler"
    affiliation   : "2"
  - name          : "Megan Merrick"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    affiliation   : "3"

@@

keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling, common ground"

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
numbersections    : false

@@

# Authornote

We thank Jacqueline Quirke and Sabina Zacco for help with the data collection and Bria Long and Gregor Kachel for comments on an earlier version of the paper. M. Bohn received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no. 749229. M. C. Frank was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition. All experiments and analyses were pre-registered (https://osf.io/u7kxe/). Stimuli, data, and analysis code are available in a public repository (https://github.com/manuelbohn/mcc).

@@
